A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
oooops

\Omit{
All non-target objects remain unchanged so the planner can
exploit object co-occurances using reliably sensed objects to
compensate for the increased sensor noise.
}

We experimented with DT sessions with initial belief-states admitting
between 20 and 100 abstract states with non-zero probability. We run
50 simulations in each configuration, and have a timeout on each
simulation of 30 minutes (1800 seconds)\footnote{All experiments were
conducted on a 2.66GHz Intel Xeon X5355 using one CPU core.}. The
continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor).

>>>>

\Omit{
All non-target objects remain unchanged so the planner can
exploit object co-occurrences using reliably sensed objects to
compensate for the increased sensor noise.
}

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Figure~\ref{fig:results-quality}, where we report
expected discounted rewards (not plan costs).
